Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Define acronyms

Experiments were performed in a turbine test bed specifically designed for
cross-flow turbines. The test bed was integrated as part of the \hl {University of New Hampshire (UNH)} 
 tow tank,
which is a 36 m-long facility with a 3.66 m-wide and 2.44 m-deep cross-section.
The turbine model used in this study was the UNH Reference Vertical Axis Turbine
(RVAT), which was designed to be a generic case for numerical model testing,
similar to the Sandia National Labs/U.S. Department of Energy RM2%please define
 River Turbine
\cite{Neary2014}, but with a higher solidity or blade chord-to-radius ratio.

>>>>

Experiments were performed in a turbine test bed specifically designed for
cross-flow turbines. The test bed was integrated as part of the University of
New Hampshire (UNH) tow tank, which is a 36 m-long facility with a 3.66 m-wide
and 2.44 m-deep cross-section. The turbine model used in this study was the UNH
Reference Vertical Axis Turbine (RVAT), which was designed to be a generic case
for numerical model testing, similar to the Sandia National Labs/U.S. Department
of Energy Reference Model 2 (RM2) River Turbine \cite{Neary2014}, but with a
higher solidity or blade chord-to-radius ratio.
